%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj + some brand new features from Mary Feofanova + /OlympiadAchievement command from Sergei Voloboev
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{20pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  linkbordercolor=red,
  urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
  \item\small{
  	\ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
  }
}

\usepackage[dvipsnames]{xcolor}
\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\olympiadAchievement}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{#1} & \textcolor{mygray}{#2}
    \end{tabular*}
}


\newcommand{\resumeExpSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
      {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeTeachingSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{#1} & \textcolor{mygray}{\textit{\small #2}}
    \end{tabular*}
}



\newcommand{\resumeProjSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Sergei Voloboev} & Email : \href{mailto:voloboeff201087@gmail.com}{voloboeff201087@gmail.com}\\
  Github: \href{https://github.com/sergeyerr}{sergeyerr} & Mobile : +49\hspace{0.5ex} 1575\hspace{0.5ex}014\hspace{0.5ex}02\hspace{0.5ex}56 \\
  Linkedin: \href{https://www.linkedin.com/in/sergei-voloboev-3138b3196/}{sergei-voloboev-3138b3196} & Spoken Languages: English -- Advanced (IELTS 7.0), Russian -- Native
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
       {Technical University of Munich}{Munich, Germany}
      {Master of Science in Data Engineering and Analytics}{Oct. 2021 - Sep. 2023 (Present)}
    \resumeSubheading
      {Perm State University}{Perm, Russia}
      {Bachelor of Applied Mathematics 
       and Computer Science, 5/5}{Sep. 2017 - Jul. 2021}
	 %\begin{comment}
	 \resumeItemListStart
        \resumeItem{Thesis}
          {Ontology-driven framework to create intelligent assistants choosing machine learning algorithms}
      \resumeItemListEnd
      %\end{comment}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeExpSubheading
      {\href{http://lab-code.com/}{Laboratory of Code}}{Perm, Russia}
      {Data Engineer}{May 2020 - Jul. 2021}
      {\skill{Python} \skill{PyTorch} \skill{Apache Airflow} \skill{Docker} \skill{JupyterHub} \skill{Kubernetes}}
      \resumeDesc{
      \begin{itemize}
          \item Built an audio denoiser by training U-Net on \href{https://github.com/snakers4/open_stt}{2,3 TB russian speech dataset  Open STT.}
          \item Established a distributed secure infrastructure for data science experiments by setting up Kubernetes cluster with distributed Airflow and JupyterHub.
      \end{itemize}}
      \resumeExpSubheading
      {\href{https://simpl-group.ru/}{Simpl}}{Perm, Russia}
      {Junior SWE}{May 2019 - Sep. 2019}
      {\skill{PySpark} \skill{Python} \skill{Alluxio} \skill{Hadoop} \skill{Docker} \skill{C\#}}
      \resumeDesc{\begin{itemize}
          \item Improved the speed of a data processing solution for oil production company by 3 times with in-memory distributed computing.
          \item Set up Apache Spark cluster on office computers using Docker and Docker Swarm.
      \end{itemize}}
       
    
  \resumeSubHeadingListEnd
%-----------TEACHING EXPERIENCE-----------------
\section{Volunteer Teaching Experience}
\resumeSubHeadingListStart
\resumeTeachingSubheading
{Held lectures and seminars on Python and machine learning for freshmen students of \href{http://mmft.psu.ru/}{PSU}.}{Sep. 2020 - Jul. 2021}
\resumeSubHeadingListEnd
%------------PROJECTS-------------------------------
\section{Projects}
  \resumeSubHeadingListStart
       \resumeProjSubheading
      {\href{https://www.helmholtz-berlin.de/events/summer-school/index_en.html}{HZB ML Hackathon 2021}}{Berlin, Germany}
      {\skill{Python} \skill{Scipy} \skill{Pytorch} \skill{HDBSCAN} \skill{Autoencoders} \skill{Matplotlib} \skill{Pandas}
      }{Sep. 2021}
          \resumeDesc{\begin{itemize}
          \item Achieved 0.87 \href{https://scikit-learn.org/stable/modules/generated/sklearn.metrics.v_measure_score.html}{V-measure} on clustering holography images from magnetic domains for labels, produced by group of physicists for 4 years period with usage of HDBSCAN clustering algorithm over VQ-VAE latent space.
           \item Spotted a pattern in magnetic fields via visual analysis of dataset's statistics, the recognition of which improved \href{https://scikit-learn.org/stable/modules/generated/sklearn.metrics.v_measure_score.html}{V-measure} by 0.2.
      \end{itemize}}
      \resumeProjSubheading
      {\href{https://github.com/sergeyerr/DCHelper_1.0}{Analytical platform with NLP intelligent assistance} [Bachelor thesis]}{Perm, Russia}
      {\skill{Python} \skill{Flask} \skill{FastAPI}  \skill{Docker} \skill{PyTorch} \skill{HuggingFace Transformers} \skill {Ontologies} \skill{PostgreSQL} \skill{JQuery}
      }{Jan. 2020 - Jul. 2021}
          \resumeDesc{
          \begin{itemize}
          \item Built a platform which provides intelligent assistance for choosing ML algorithms from multiple environments (Python, Weka, R), considering user's preferences and the metadata of the processed dataset.
           \item Developed an algorithm for the system's smart search and chat bot both with 0.9 F-score that uses ontologies and sentence BERT.
         \end{itemize}}
  
    \resumeProjSubheading
      {\href{https://github.com/sergeyerr/Stonxygen-final-lab-distributed_systems-}{Distributed stocks portfolio application}}{Perm, Russia}
      {\skill{Python} \skill{gRPC} \skill{PostgreSQL} \skill{Redis} \skill{RabbitMQ} \skill{Docker} \skill{Docker swarm} \skill{Nginx} \skill{AWS}}{Dec. 2020}
          \resumeDesc{
          \begin{itemize}
          \item  Designed the architecture of the application for the final team project of a distributed systems course, which required usage of multiple languages and communication technologies, network reliability and fault tolerance.  
           \item Deployed the system on 5 AWS instances and tested its overall reliability.
         \end{itemize}}
    
      
  \resumeSubHeadingListEnd

\section{\href{https://drive.google.com/drive/folders/1vUF3QtK-Zzw8Dii6tyzjPJVz3CriXiuV?usp=sharing}{Achievements}}
  \resumeSubHeadingListStart
     \olympiadAchievement
           {ML2R Autumn School 2021, \href{https://drive.google.com/file/d/1jenRziG0iAKluF8k_sz2TIEIWkR7dboS/view}{Compactness award} (Technical University of Dortmund)}{Dortmund, Germany}
    \olympiadAchievement
           {RuCode Festival, \href{https://drive.google.com/file/d/1jEML6AG0DPXquMBWrjFpnHZ6aQALPAFK/view?usp=sharing}{AI track 2021 prize-winner} (Moscow Institute of Physics and Technology)}{Moscow, Russia}
    \olympiadAchievement
           {"I am professional" All-Russian Olympiad, \href{https://drive.google.com/file/d/14g7DC5SCxy9ZNuK5HXsbeg5r65SKvT5h/view?usp=sharing}{AI track 2020 winner}; \href{https://drive.google.com/file/d/1k_xNKaxvC_3RWOU5Op7_NdgnLTQ6Eelz/view?usp=sharing}{2021 prize-winner} (Yandex) }{Moscow, Russia}
    \olympiadAchievement
           {ICPC Northern Eurasia Finals Honorable Mentions. \href{https://drive.google.com/file/d/1IrXh3PwWHBxdfocmYWjzRASLg_Rr3gct/view?usp=sharing}{2018-2019}; \href{https://drive.google.com/file/d/1kuG2RhoS5X3fyA5QnYjSmqe6M1bqurwr/view?usp=sharing}{2019-2020}}{St. Petersburg, Russia}
    \olympiadAchievement
           {Xsolla Hackathon 2019, \href{https://drive.google.com/file/d/1Yp3cZBoLz1Qezf5iNeWDabhyUloOD40q/view?usp=sharing}{1st place}}{Perm, Russia}
   
          
  \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: \textit{(advanced)} Python, C++, C\#; \textit{(basics)} JavaScript, Java, Kotlin, Go }
   }\vspace{-7pt}
   \item{
     \textbf{Technologies}{: \textit{(advanced)} Docker (Swarm), PostgeSQL; \textit{(basics)} Kubernetes, Git, AWS, Google Cloud, Linux, Tableau}
   }
   \vspace{-7pt}
   \item{
     \textbf{Knowledge}{: \textit{(advanced)} Algorithms, Data Structures, Machine Learning, NLP; \textit{(basics)} Cloud Computing, Software Design}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
